Usable Security in Virtual Power Plants

### 2018-01-25 acmart-master/draft.tex
More Fine Tunings

Critical infrastructures are integral to the functioning of our daily lives. They are changing in order to solve different problems it faces nowadays. The growth of power demand, integration of markets and the need of sustainable and efficient energy sources. \\
One such important critical infrastructure is the smart grid. A typical smart grid is divided into several domains such as generation, transmission and distribution. All the actors within domains of a smart grid are connected through information and communication technology(ICT). Hence, energy grids have continuously been the target of cyber attacks and provided their use of standard architecture and internet, they are relatively easier to attack. Security mechanisms have been introduced to protect against such attacks. Security-by-design approach has been used to determine security measures for various systems during design phase. With this approach, the system is equipped to deal with difficult scenarios before deployment. \\ However, there may be instances where the operator must intervene to control the system when under attack and stress. During such instances, the user maybe asked to re-authenticate themselves, at which point remembering increasingly difficult passwords and entering it correctly actually causes an overhead on the operator. The security mechanism in fact is a hindrance here. Such a situation could be avoided if the authentication system in place is usable under different conditions.

\section{Related Work}
Usability of security is an area of research that has been largely ignored. More focus has been placed on security itself, hence the presence of extensive literature on security in information systems and lack thereof in the case of usability. Smart grid is a vast interconnection of several different kinds of components across several domains. There are several key components that interact with each other that expose several vulnerabilities\cite{liu2012cyber}. There are several vulnerabilities across communication protocols, legacy devices and technologies. Additionally, when designing a system, new vulnerabilities may be found, rendering current security infrastructure weaker. A cyber-physical approach\cite{mo2012cyber} has been presented to tackle new security challenges. They propose a system model using security requirements and vulnerabilities to identify countermeasures. In order to identify security requirements, a concrete network architecture is required. From the architecture, security objectives can be derived and threats can be evaluated to determine the requirements for security. Wang et. al\cite{wang2013cyber} provide a comprehensive categorization and evaluation of network threats and discuss their countermeasures in detail.
\newline 
There is a lack of usability standards that determine the goals of usability for energy systems. Usability is not directly engineered, but is rather a consequence of system engineering. There are guidelines that aid engineers in developing usable systems\cite{nurse2011guidelines}. Standards such as ISO 9241-11\cite{bevan2015iso} state that usability must be measured in terms of effectiveness, efficiency and satisfaction. These terms must be related to the system of interest using performance metrics of the respective system. A first look at such a relation is provided\cite{kainda2010security}, however is not comprehensive enough to establish a concrete relation between systems. In this paper, we build on this idea to derive a usable security by design approach that begins at the design phase\cite{nielsen1992usability}. The goal of this research to establish how usability of security in power plants can be achieved. A second goal is to reduce the burden on a power plant operator, since the operation of a power plant can be stressful. We assume that the operator of the power plant is oblivious to the security design. Additionally, we assume there is an authentication system in place whose goal is to protect the system and authenticate legitimate operators and is expected to function with high efficiency. We shall focus only on security and usability and their relation. Hence, usability of other systems are not considered. Only systems having an user interface are considered.

@@

Virtual Power Plant(VPP) is one such infrastructure. A VPP is a centralized system that aggregates various energy sources to meet the energy demand of a geographical area. It relies upon software to remotely control, optimize and dispatch energy from Distributed Energy resources(DERs). At the heart of every VPP is the Energy Management System(EMS). The EMS manages power flows in order to minimize the electricity generation costs and avoid loss of energy produced by generators based on renewable energy sources. The EMS consists of a set of software programs designed to control and monitor several aspects of the power plant such as generation levels, capacity, current and voltage levels, power fluctuations, supply-demand matching and so on. These software programs are automated and carry out operations based on pre-defined rules and functions. They are consistently monitored by an operator, known as VPP Operator. Therefore, a VPP is a system that employs software and networking tools making it susceptible to cyber attacks. There are several known ways to attack a power plant, network based attacks such as man-in-the-middle, Masquerading, Spoofing, Denial of service, Injection etc, software vulnerability based attacks, hardware based attacks and so on. Most of the known attacks have defined countermeasures which are in use to protect the power plant. Even with the presence of an extensive defense infrastructure, there may be new and unprecedented attacks on power plants, including those that exploit zero-day vulnerabilities. 
\newline
A virtual power plant under attack is expected to continue functioning normally, i.e, it must primarily meet the goal of availability to the customer end. In anticipation of such attacks, the system may be configured to reschedule, find replacement sources or even attempt to control the system to prevent its shutdown or damage. The operator may be requested to control the system in case of unprecedented events or cases where the operator's intervention or authorization are required. For example, consider a scenario when a power plant is under attack and its primary generation units are inaccessible. The VPP then attempts to find replacement units. However, in case of a large scale attack units in the neighbourhood may also be rendered inaccessible. Therefore, the VPP may have to look for units outside its allotted area which may require operator request and authorization. In such a case, the operator is required to access and operate the system. We assume there is an authentication mechanism in place that protects the system from unauthorized access, and therefore is the first interface the operator comes across. This authentication interface is vital since it prevents unauthorized personnel from accessing the system either in normal system state or when the system is under attack, which could be orchestrated by the unauthorized personnel themselves. The authentication mechanism should however be a usable mechanism, even under stress, to prevent the legitimate power plant operator from being locked out. A traditional username-password system in this case could potentially be a problem. The operator is required to recall and enter the information accurately in order to be granted access. In such a situation, the operator may find it difficult to recall a complex password and is more likely to make mistakes entering it and being denied access, which could lead to a catastrophe.

@@

Traditional authentication mechanisms are largely based on password based systems. Having a long random password is good advice. Unfortunately, when faced with having to remember several random fifteen character passwords (characters being A to Z, a to z, 0 to 9 and an assortment of other printable characters such as ! @ \# \$ and \%), most users apply a judgement to the value of the information protected by the password and act accordingly. 
Secure passwords may be constructed from a combination of alphabets, numbers and symbols. There is a trade off though, as such passwords are harder to remember and also hard to enter into a system without errors. It is also compounded by the fact that users are recommended to change passwords periodically. Users tend to create variations of their previous passwords to prevent having to generate a new password and consider using a variant of a previous password easier since they are already familiar with it. This is especially problematic since users may forget the password has been changed and do not remember the new password, inviting a lot of pressure onto users who are not technologically friendly and are oblivious to the system structure. Therefore, the most secure passwords and password systems are, in fact, the least usable.

@@

Therefore, with usability and security being a trade-off, organizations often prioritize security over usability. Hence, to bridge this gap between the two, a framework is required. A framework which can unite the two and allow a system to be secure as well as usable. In the next section, we look towards such a usable security framework. Since the focus is usability, we consider authentication mechanisms, which are security mechanisms in place that are directly interfaced by an operator. Most other security mechanisms affect software and hardware performance but do not impact usability and user performance since there is no existing interface to the security infrastructure.

@@

Usability is a measure of the interactive user experience associated with a user interface, such as a website or software application. A user-friendly interface design is easy-to-learn, supports users' tasks and goals efficiently and effectively, and is satisfying and engaging to use.
\newline
An interface's level of usability can be measured by inviting intended users of the system to participate in a usability testing session. During a usability test session, a user is given a series of tasks to complete by using the system in question, without any assistance from the researcher. The researcher records user behaviours, emotional reactions, and the user's performance as they attempt to accomplish each task. The researcher takes note of any moments of confusion or frustration that the user experienced while trying to complete a task and also tracks whether or not the user was able to satisfactorily complete each task. Analysis of data from several users provides User Experience Engineers a means of recommending how and where to re-design the interface in order to improve its level of usability and thus, the user experience in general.

@@

Usability depends on a number of factors including how well the functionality fits the user needs, how well the flow through the application fits user tasks and how well the response of the application fits user expectations. For a power plant operator, the system must be easy to understand and easy to use. The operator is not expected to understand how the system is built or functions, but is expected to interface well with the said system. 
\newline
From a plant operator's perspective, usability is important because it can make the difference between performing a task accurately and completely or not. From the developer's perspective, usability is important because it can mean the difference between the success or failure of a system. From a management point of view, software with poor usability can reduce the productivity of the workforce to a level of performance worse than without the system. In all cases, lack of usability can cost time and effort and can greatly determine the success or failure of a system.

@@

The key principle for maximizing usability is to employ iterative design, which progressively refines the design through evaluation from the early stages of design. The evaluation steps enable the designers and developers to incorporate user and client feedback until the system reaches an acceptable level of usability. Achieving a high level of usability requires focusing design efforts on the intended end-user of the system. Power Plant operator feedback will be vital. Due to the fact that the operators manage a critical infrastructure, their feedback will be different and more specific when compared to other systems. A step forward would be to take the existing system, consider the operator feedback on usability and task information together to build a usable security framework.

@@

\section{Framework for Usable Security}
In the previous section, usability was explained as a broad concept. It is applicable to any system which is directly interfaced by a user or has an impact on user perforamnce. In this section, we specialize the usability concept to security in virtual power plants and as will further be explained, to authentication mechanisms.\\ Since, usability and security are normally at opposite ends of the spectrum, there are no uniform set of criteria or guidelines that define a usable security system. Nurse et al\cite{nurse2011guidelines} compiled a list as guidelines for usable security.
\newline
To design a security system that is usable, we need appropriate metrics to measure its performance, especially in context of virtual power plants. Therefore, we need to define such metrics. With the security system in focus, the usability metrics must stem from the properties of security themselves. Since the security system is designed for virtual power plants, some factors are automatically constrained. Due to the volatile nature of power plants, time is of utmost importance. Hence, a time efficient system is a requirement. We also need to consider the performance of the operator under stress. A well designed system reduces operator responsibilities like memory use for passwords and encourages productivity. Through this process, we then develop a security with a view of usability in the design stage itself, rather than first building a security system and then attempting to incorporate usability. When designing a security system, each interface of security could be tested for its usability wherever applicable. A less usable component may affect usability of another. The issue at hand is that due to the lack of usability metrics or any quantifiable value, any system cannot yet be defined as usable or unusable. \\

@@

\subsection{Validation of the framework}
To demonstrate how this framework could be used, we use an example. Two different authentication systems were tested, a fingerprint matching system and a simple password system. The evaluation involved participants using both types of systems and then answering a questionnaire. To assess fingerprint matching, two approaches were used. Since there are several types of fingerprint matching algorithms, performance may vary. Therefore, the most common implementations found in real life were used. First, an optical scanner of fingerprints was evaluated. An optical scanner scans the fingerprint into an optical image and compares the image as is with a database of images. This process is slow and less secure, as images of fingerprints are stored unprotected in the database. The second kind was a capacitive scanner, where fingerprints are read using varying electric charges when a ridge comes in contact with the scanner. This change is charge is converted to digital data, which is then analysed to look for unique features. Data is stored digitally, though not necessarily encrypted. This form of storing data is still vulnerable but more secure than images. There were 30 participants whose fingerprints were added to a database of more than 1000 entries. The results of the capacitive scanner were found to be more optimal. They are shown below:

\begin{center}
\begin{table}[H]
\caption{Results for Biometric systems.}
\label{tab:result1}
\resizebox{9cm}{!}{
\begin{tabular}{|c|c|}
\hline
\textbf{Security Metric} & \textbf{Observed values} \\
\hline
EER & 3.9\%\\
\hline
Accuracy & 96.1\%. \\
\hline
Task Completion Time & Average of 1.8 seconds \\
\hline
Interface Design & 4.2\\
\hline
Memory Load & 5\\
\hline
\end{tabular}
}
\end{table}
\end{center}

>>>>

Critical infrastructures are integral to the functioning of our daily lives. They are changing in order to solve different problems it faces nowadays. The growth of power demand, integration of markets and the need of sustainable and efficient energy sources. \\
One such important critical infrastructure is the smart grid. A typical smart grid is divided into several domains such as generation, transmission and distribution. All the actors within domains of a smart grid are connected through information and communication technology(ICT). Hence, energy grids have continuously been the target of cyber attacks and provided their use of standard architecture and internet, they are relatively easier to attack. Security mechanisms have been introduced to protect against such attacks. Security-by-design approach has been used to determine security measures for various systems during design phase. With this approach, the system is equipped to deal with difficult scenarios before deployment. \\ However, there may be instances where the operator must intervene to control the system when under attack and stress. During such instances, the user maybe asked to re-authenticate themselves, at which point remembering increasingly difficult passwords and entering it correctly actually causes an overhead on the operator. The security mechanism in fact is a hindrance here. Such a situation could be avoided if the authentication system in place is usable under different conditions. The rest of the paper is organized as the following, section 2 highlights the related work and section 3 overviews security in virtual power plants and certain issues. Section 4 describes the concept of usability and its importance in critical infrastructures like virtual power plants. In section 5 we introduce our contribution, a framework to assess usability of security and together with section 6 described how this framework can be utilized. Section 7 covers the conclusion and future work.

\section{Related Work}
Usability of security is an area of research that has been largely ignored. More focus has been placed on security itself, hence the presence of extensive literature on security in information systems and lack thereof in the case of usability. Smart grid is a vast interconnection of several different kinds of components across several domains. There are several key components that interact with each other that expose several vulnerabilities~\cite{liu2012cyber}. There are several vulnerabilities across communication protocols, legacy devices and technologies. Additionally, when designing a system, new vulnerabilities may be found, rendering current security infrastructure weaker. A cyber-physical approach~\cite{mo2012cyber} has been presented to tackle new security challenges. They propose a system model using security requirements and vulnerabilities to identify countermeasures. In order to identify security requirements, a concrete network architecture is required. From the architecture, security objectives can be derived and threats can be evaluated to determine the requirements for security. Wang et. al~\cite{wang2013cyber} provide a comprehensive categorization and evaluation of network threats and discuss their countermeasures in detail.
\newline 
There is a lack of usability standards that determine the goals of usability for energy systems. Usability is not directly engineered, but is rather a consequence of system engineering. There are guidelines that aid engineers in developing usable systems~\cite{nurse2011guidelines}. Standards such as ISO 9241-11~\cite{bevan2015iso} state that usability must be measured in terms of effectiveness, efficiency and satisfaction. These terms must be related to the system of interest using performance metrics of the respective system. A first look at such a relation is provided~\cite{kainda2010security}, however is not comprehensive enough to establish a concrete relation between systems. In this paper, we build on this idea to derive a usable security by design approach that begins at the design phase~\cite{nielsen1992usability}. The goal of this research to establish how usability of security in power plants can be achieved. A second goal is to reduce the burden on a power plant operator, since the operation of a power plant can be stressful. We assume that the operator of the power plant is oblivious to the security design. Additionally, we assume there is an authentication system in place whose goal is to protect the system and authenticate legitimate operators and is expected to function with high efficiency. We shall focus only on security and usability and their relation. Hence, usability of other systems are not considered. Only systems having an user interface are considered.

@@

Virtual Power Plant(VPP) is one such infrastructure~\cite{pudjianto2007virtual}. A VPP is a centralized system that aggregates various energy sources to meet the energy demand of a geographical area. It relies upon software to remotely control, optimize and dispatch energy from Distributed Energy resources(DERs). At the heart of every VPP is the Energy Management System(EMS). The EMS manages power flows in order to minimize the electricity generation costs and avoid loss of energy produced by generators based on renewable energy sources. The EMS consists of a set of software programs designed to control and monitor several aspects of the power plant such as generation levels, capacity, current and voltage levels, power fluctuations, supply-demand matching and so on. These software programs are automated and carry out operations based on pre-defined rules and functions. They are consistently monitored by an operator, known as VPP Operator. Therefore, a VPP is a system that employs software and networking tools making it susceptible to cyber attacks. There are several known ways to attack a power plant, network based attacks such as man-in-the-middle, Masquerading, Spoofing, Denial of service, Injection etc, software vulnerability based attacks, hardware based attacks and so on. Most of the known attacks have defined countermeasures which are in use to protect the power plant. Even with the presence of an extensive defense infrastructure, there may be new and unprecedented attacks on power plants, including those that exploit zero-day vulnerabilities. 
\newline
A virtual power plant under attack is expected to continue functioning normally, i.e, it must primarily meet the goal of availability to the customer end. In anticipation of such attacks, the system may be configured to reschedule, find replacement sources or even attempt to control the system to prevent its shutdown or damage. The operator may be requested to control the system in case of unprecedented events or cases where the operator's intervention or authorization are required. For example, consider a scenario when a power plant is under attack and its primary generation units are inaccessible. The VPP then attempts to find replacement units. However, in case of a large scale attack units in the neighbourhood may also be rendered inaccessible. Therefore, the VPP may have to look for units outside its allotted area which may require operator request and authorization. In such a case, the operator is required to access and operate the system. We assume there is an authentication mechanism in place that protects the system from unauthorized access, and therefore is the first interface the operator comes across. This authentication interface is vital since it prevents unauthorized personnel from accessing the system either in normal system state or when the system is under attack, which could be orchestrated by the unauthorized personnel themselves. The authentication mechanism should however be a usable mechanism, even under stress, to prevent the legitimate power plant operator from being locked out. A traditional username-password system in this case could potentially be a problem. The operator is required to recall and enter the information accurately in order to be granted access. In such a situation, the operator may find it difficult to recall a complex password and is more likely to make mistakes entering it and being denied access, which could lead to a catastrophe.

@@

Traditional authentication mechanisms are largely based on password based systems. Having a long random password is good advice. Unfortunately, when faced with having to remember several random fifteen character passwords (characters being A to Z, a to z, 0 to 9 and an assortment of other printable characters such as ! @ \# \$ and \%), most users apply a judgement to the value of the information protected by the password and act accordingly. 
Secure passwords may be constructed from a combination of alphabets, numbers and symbols~\cite{adams1999users,verheul2007selecting}. There is a trade off though, as such passwords are harder to remember and also hard to enter into a system without errors. It is also compounded by the fact that users are recommended to change passwords periodically. Users tend to create variations of their previous passwords to prevent having to generate a new password and consider using a variant of a previous password easier since they are already familiar with it. This is especially problematic since users may forget the password has been changed and do not remember the new password, inviting a lot of pressure onto users who are not technologically friendly and are oblivious to the system structure. Therefore, the most secure passwords and password systems are, in fact, the least usable.

@@

Therefore, with usability and security being a trade-off, organizations often prioritize security over usability. Hence, to bridge this gap between the two, a framework is required. A framework which can unite the two and allow a system to be secure as well as usable across different situations. In the next section, we look towards a framework to assess usability of security. We consider authentication mechanisms, which are security mechanisms that are directly interfaced by an operator. Most other security mechanisms affect software and hardware performance but do not impact usability and user performance since there is no existing interface to the security infrastructure.

@@

Usability is a measure of the interactive user experience associated with a user interface, such as a website or software application. A user-friendly interface design is easy-to-learn, supports users' tasks and goals efficiently and effectively, and is satisfying and engaging to use.
\newline
An interface's level of usability can be measured by inviting intended users of the system to participate in a usability testing session. During a usability test session, a user is given a series of tasks to complete by using the system in question, without any assistance from the researcher. The researcher records user behaviours, emotional reactions, and the user's performance as they attempt to accomplish each task. The researcher takes note of any moments of confusion or frustration that the user experienced while trying to complete a task and also tracks whether or not the user was able to satisfactorily complete each task. Analysis of data from several users provides user experience engineers a means of recommending how and where to re-design the interface in order to improve its level of usability and thus, the user experience in general.

@@

Usability depends on a number of factors including how well the functionality fits the user needs, how well the flow through the application fits user tasks and how well the response of the application fits user expectations. For a power plant operator, the system must be easy to understand and easy to use. The operator is not expected to understand how the system is built or functions, but is expected to interface well with the system. 
\newline
From a plant operator's perspective, usability is important because it can make the difference between performing a task accurately and completely or not. From the developer's perspective, usability is important because it can mean the difference between the success or failure of a system. From a management point of view, software with poor usability can reduce the productivity of the workforce to a level of performance worse than without the system. In all cases, lack of usability can cost time and effort and can greatly determine the success or failure of a system.

@@

The key principle for maximizing usability is to employ iterative design, which progressively refines the design through evaluation from the early stages of design. The evaluation steps enable the designers and developers to incorporate user and client feedback until the system reaches an acceptable level of usability. Achieving a high level of usability requires focusing design efforts on the intended end-user of the system. Power Plant operator feedback will be vital. Due to the fact that the operators manage a critical infrastructure, their feedback will be different and more specific when compared to other systems. A step forward would be to take the existing system, consider the operator feedback on usability and task information together to build a framework for usability of security.

@@

\section{Framework for Usability of Security}
In the previous section, usability was explained as a broad concept. It is applicable to any system which is directly interfaced by a user or has an impact on user perforamnce. In this section, we specialize the usability concept to security in virtual power plants and as will further be explained, to authentication mechanisms.\\ Since, usability and security are normally at opposite ends of the spectrum, there are no uniform set of criteria or guidelines that define a usable security system. Nurse et al.~\cite{nurse2011guidelines} compiled a list as guidelines for usable security.
\newline
To design a security system that is usable, we need appropriate metrics to measure its performance, especially in context of virtual power plants. Therefore, we need to define such metrics. With the security system in focus, the usability metrics must stem from the properties of security themselves. Since the security system is designed for virtual power plants, some factors are automatically constrained. Due to the volatile nature of power plants, time is of utmost importance. Hence, a time efficient system is a requirement. We also need to consider the performance of the operator under stress. A well designed system reduces operator responsibilities like memory use for passwords and encourages productivity. Through this process, we then develop a security with a view of usability in the design stage itself, rather than first building a security system and then attempting to incorporate usability. When designing a security system, each interface of security could be tested for its usability wherever applicable. A less usable component may affect usability of another. The issue at hand is that due to the lack of usability metrics or any quantifiable value, no system can yet be defined as usable or unusable. \\

@@

\subsection{Validation of the framework}
To demonstrate how this framework could be used, we use an example. Two different authentication systems were tested, a fingerprint matching system and a simple password system. The evaluation involved participants using both types of systems and then answering a questionnaire. To assess fingerprint matching, two approaches were used. Since there are several types of fingerprint matching algorithms, performance may vary. Therefore, the most common implementations found in real life were used. First, an optical scanner of fingerprints was evaluated. An optical scanner scans the fingerprint into an optical image and compares the image as is with a database of images. This process is slow and less secure, as images of fingerprints are stored unprotected in the database. The second kind was a capacitive scanner, where fingerprints are read using varying electric charges when a ridge comes in contact with the scanner. This change is charge is converted to digital data, which is then analysed to look for unique features. Data is stored digitally, though not necessarily encrypted. This form of storing data is still vulnerable but more secure than images. There were 30 participants whose fingerprints were added to a database of more than 1000 entries. The results of the capacitive scanner were found to be better and efficient when compared to that of optical scanner. They are shown below:

\begin{center}
\begin{table}[H]
\caption{Results for fingerprint recognition using capacitive scanner.}
\label{tab:result1}
\resizebox{9cm}{!}{
\begin{tabular}{|c|c|}
\hline
\textbf{Security Metric} & \textbf{Observed values} \\
\hline
EER & 3.9\%\\
\hline
Accuracy & 96.1\%. \\
\hline
Task Completion Time & Average of 1.8 seconds \\
\hline
Interface Design & 4.2\\
\hline
Memory Load & 5\\
\hline
\end{tabular}
}
\end{table}
\end{center}

### 2018-01-25 acmart-master/sample-sigconf-authordraft.tex
More changes
More Fine Tunings

\usepackage{booktabs} % For formal tables
\usepackage{tabularx}
\usepackage{makecell}
\usepackage{tikz}
\usepackage{pgf-umlsd}
\usepgflibrary{arrows}
\usetikzlibrary{calc}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

@@

\begin{abstract}
Automation of systems requires users to be less involved in system control. During situations when the user must interface with the system by themselves, the technology available must assist the user to complete their task and must not be a hindrance. Therefore, it is necessary to make the system more usable. Usability is often overlooked in favour of primary system goals, hence the lack of advancement in the usability drive. There exists no concrete framework to assess usability of a system, since most existing approaches focus on user feedback and neglect system optimization. In this study, usability is described in context of security in virtual power plants. A usability framework was established for authentication mechanisms. It was determined that usability arises by optimizing system factors that relate to usability standards with the crucial addition of user preferences. Additionally, the approach can be applied to any target system to assess usability.
\end{abstract}

>>>>

\usepackage{booktabs} % For formal tables
\usepackage{tabularx}
\usepackage{makecell}
\usepackage{tikz}
\usepackage{pgf-umlsd}
\usepgflibrary{arrows}
\usetikzlibrary{calc}
\usepackage{amsmath}
\usepackage{amssymb}
% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

@@

\begin{abstract}
Power grid systems deliver electricity from suppliers that generate power to customers
including private homes, corporations and public domain. The transmission takes place
through electric grids and networks that span across geographical areas. Smart grids utilize information and communication technology to perform the required functions where
SCADA(Supervisory Control And Data Acquisition) systems monitor, control and manage
the processes in critical infrastructures. They include Virtual Power Plants(VPPs) that
schedule energy sources appropriately to meet the energy demand. Dynamic Virtual Power
Plants(DVPPs) have been proposed to decentralize VPPs to make energy scheduling more
flexible. As with any critical infrastructure, attacks on VPPs and DVPPs could result in
catastrophic situations. Security is required in place to defend the system against attacks. However, security mechanisms such as authentication systems may actually prevent the operator from gaining access to the system in time to control the power plant. In such a case, security is actually a hindrance. The authentication mechanism must be more usable from the perspective of the operator, even under stressful situations. Therefore, the aim of this paper is to establish a method to approach usable security by design.
\end{abstract}
